Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-27 doc/manuscript/ESSDmanuscript.Rmd
add FAO ecozone codes
https://www.fao.org/3/ad652e/ad652e10.htm

closes #33

```{r fig_map, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Map of sites in ForC shaded by number of records relevant to (circles) and transferred to (triangles) EFDB.} Symbols are colored according to the number of records at each site. Underlying map shows FAO ecozones, which are coded as follows: ...."}
#this is for a two-column figure. for one-column figure, use out.width = "8.3cm"
knitr::include_graphics("figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent.png")
```

>>>>

```{r fig_map, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Map of sites in ForC shaded by number of records relevant to (circles) and transferred to (triangles) EFDB.} Symbols are colored according to the number of records at each site. Underlying map shows FAO ecozones, which are coded as follows: Ba-Boreal coniferous forest, Bb-Boreal tundra woodland, BM-Boreal mountain systems, P-Polar, SBSh-Subtropical steppe, SBWh-Subtropical desert, SCf-Subtropical humid forest, SCs-Subtropical dry forest, SM-Subtropical mountain systems, TAr-Tropical rain forest,  TAwa-Tropical moist deciduous forest, TAwb-Tropical dry forest, TBSh-Tropical shrubland, TBWh-Tropical desert, TeBSk-Temperate steppe, TeBWk-Temperate desert, TeDc-Temperate continental forest, TeDo-Temperate oceanic forest, TeM-Temperate mountain systems, TM-Tropical mountain systems."}
#this is for a two-column figure. for one-column figure, use out.width = "8.3cm"
knitr::include_graphics("figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent.png")
```

### 2022-04-27 doc/manuscript/ESSDmanuscript.tex
add FAO ecozone codes
https://www.fao.org/3/ad652e/ad652e10.htm

closes #33

\begin{figure}
\includegraphics[width=15cm]{figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent} \caption{\textbf{Map of sites in ForC shaded by number of records relevant to (circles) and transferred to (triangles) EFDB.} Symbols are colored according to the number of records at each site. Underlying map shows FAO ecozones, which are coded as follows: ....}\label{fig:fig_map}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=15cm]{figures_tables/World_Map_of_sites_with_FAO_and_IPCC_data_sent} \caption{\textbf{Map of sites in ForC shaded by number of records relevant to (circles) and transferred to (triangles) EFDB.} Symbols are colored according to the number of records at each site. Underlying map shows FAO ecozones, which are coded as follows: Ba-Boreal coniferous forest, Bb-Boreal tundra woodland, BM-Boreal mountain systems, P-Polar, SBSh-Subtropical steppe, SBWh-Subtropical desert, SCf-Subtropical humid forest, SCs-Subtropical dry forest, SM-Subtropical mountain systems, TAr-Tropical rain forest,  TAwa-Tropical moist deciduous forest, TAwb-Tropical dry forest, TBSh-Tropical shrubland, TBWh-Tropical desert, TeBSk-Temperate steppe, TeBWk-Temperate desert, TeDc-Temperate continental forest, TeDo-Temperate oceanic forest, TeM-Temperate mountain systems, TM-Tropical mountain systems.}\label{fig:fig_map}
\end{figure}
